Impact ionization processes in a photodriven Mott insulator: influence of phononic dissipation

### 2022-11-02 resub_PRB/letters/reply_to_referees_jan.txt

Dear Dr. Kancharla,

Thank you very much for your e-mail from October 24th with the reply of the Referees on our paper. The first Referee recommends publication without hesitation. The second Referee believes that the paper has to be published in Physical Review B, discussing the points he raised.

In the new version of our paper we have taken into account in detail all comments. A detailed reply is also included to this letter.

We hope that our paper is now suitable for publication in Phys. Rev. B.

Yours sincerely,
Paolo Gazzaneo, Tommaso Maria Mazzocchi, Jan Lotze and Enrico Arrigoni

--------------------------------------------------
          First Referee                          
--------------------------------------------------

1. As the authors pointed out the electric field amplitude considered
in this paper is several orders of magnitude larger than that of the
sunlight, therefore, strictly speaking the results presented in the
present paper are more applicable to intense laser-light
photoexcitations

2. The authors have made an effort to extrapolate in the regime of
smaller electric field amplitude and smaller hybridization strength.
They note that in order to achieve the latter one would need to
several layers where photexcited carriers separated by an electric
field gradient would have more time to induce impact ionization before
escaping into the leads.

3. The authors plan in future investigation to address the previously
mentioned issue.

A1-A2-A3: We thank the Referee a lot for his remarks on and acknowledgement of our article.

4. I would like to suggest that, perhaps, the authors, in their future
investigations, could include the role of "bad" metallic contacts,
maybe represented by narrow-band leads or possibly with a small-width
insulating barrier between the leads and the material as abstracted by
the Hubbard-like model studied. If the insulating barrier is
microscopically small the carriers would still be able to tunnel, but
perhaps would remain longer in the region of the material which might
allow II to occur.

A4: We will keep this suggestion in mind for our future investigations.

----------------------------------------------------
        Second Referee                              
----------------------------------------------------

************************************************************************
*** To highlight the changes in the main text we marked them in BLUE ***
************************************************************************

1. It is really important to discuss why DMFT approximation is
expected to be meaningful in quasi-2D case (1-layer Hubbard model
coupled to leads).

A1: The Referee is right, we acknowledge that a discussion on the meaningfulness of the DMFT approximation for the quasi-2D case is missing.

In the quasi-2D case we address, the use of DMFT which neglects the momentum dependence of the electron self-energy leads to meaningful results for two main reasons.

First: The physical system we want to model with our setup is not "strictly" two dimensional, meaning that there is still some dispersion in the third dimension, even though it may be weak. For such quasi-2D systems DMFT can yield useful results (Phys. Rev. B 97, 115113 (2018)).

Second: In our treatment we do not include nonlocal correlations which give rise to long-ranged collective excitations such as magnons. Including nonlocal correlations leads to truly nonlocal effects and therefore nonlocal contributions in the self-energy, whose momentum-dependence then clearly has to be taken into account. In low dimensional systems, like the one we are considering, these effects are usually not negligible. Yet their inclusion is also a matter of choice, depending on the physics one is interested in: to clearly address the influence of the leads and acoustic phonons on impact ionization processes, spatially nonlocal correlations would complicate the overall picture and understanding.

As asked, we added in Sec. I a discussion on this point, with a reference to a comprehensive review of nonlocal correlations beyond DMFT [Rev. Mod. Phys. 90, 025003 (2018)].

2. It seems that chosen temperature is pretty high. Please discuss why
optical phonons are neglected.

A2:

We thank the Referee for raising this point, giving us the opportunity for further clarification.

The value of the temperature of T=0.02 is not high compared with the other characteristic energy scales of the system, e.g. the soft cutoff of the acoustic phonon frequency w_ph=0.1 and the Hubbard interaction U=12. It is actually the smallest chosen energy scale. Usually, the optical phonon modes energy is at least twice that of the acoustic phonons one [see Figs. 4 and 5 in Phys. Rev. B 102, 245104 (2020)]. Therefore the choice of a small value for the temperature justifies in our view taking into account only acoustic phonons and neglecting optical phonons.

Just as a remark, we are interested in the effects of phonon-mediated dissipation and for this purpose the acoustic phonons with a finite bandwidth, in contrast to optical phonons, are more effective in energy dissipation, as is already mentioned in Sec. II (there optical phonons are denoted Holstein phonons).

As the Referee suggests, we inserted a footnote in Sec. IV, addressing this point explicitly.

3. It is naturally expected that phonons reduce the bandgap (here,
pseudogap), as in standard semiconductors, where the phonons give
10-100meV reduction of the gap and the effect increases with
temperature. Strictly speaking, to obtain the change of the
bandstructure due to phonons one needs to calculate the Fan and DW
terms of the, generally speaking, momentum-dependent electron
self-energy. In this sense, again, how important are momentum
dependencies of electron Sigma in 2D case?

A3: We thank the Referee for pointing out a similar effect of reduced pseudogaps in semiconductors and for the clarification about the phonon renormalization of the band structure due to a momentum-dependent self-energy. This is an important point and we address it below.

The importance of the momentum dependence of the electron self-energy in the 2D case depends on the level of sophistication one wants to achieve in considering acoustic phonons and therefore whether one wants quantitative results or is content with qualitative results. As explicitly stated in Sec. I, "...our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work."
At this level, having used the DMFT approximation and therefore considered momentum-independent self-energies, we cannot quantify the importance of momentum dependencies in the electron self-energy.
However, as pointed out in the review Rev. Mod. Phys. 89, 015003 (2017), the Fan term is also "...traditionally referred to as the self-energy in the Migdal approximation". This is exactly the term we included, albeit without momentum dependence, to take into account the effect of the acoustic phonons on electrons. In the same review it is noted that the Debye-Waller term is static, i.e. independent of frequency. Hence within DMFT, it would correspond to a change in the chemical potential. Since we consider the particle-hole symmetric case, the Debye-Waller term does not contribute.

We included a footnote in Sec. III.B addressing the momentum-dependence, together with a reference to the review mentioned above [Rev. Mod. Phys. 89, 015003 (2017)].

4. It is not clear from Conclusions (at least for me) what stopped the
authors to consider more realistic weaker fields and hybridizations.

A4:

We thank the Referee for having brought up this important point.

We did not consider weaker electric field amplitudes since DMFT only converges slowly for such a choice of parameters. We have already discussed this point in the footnote [47]. The same reasoning applies for smaller hybridization strength which slows down the convergence of the DMFT cycle considerably.

We followed the suggestion of the Referee, moving the footnote [47] into the main text in Sec. V and extending it to mention smaller hybridizations.

List of changes:

**********************************************************************************************
*** To highlight the changes we marked them in BLUE (in source code denoted by '\resub{}') ***
**********************************************************************************************

Motivated by questions/observations from Second Referee:

Modified Sec. I  
Added reference in Sec. I
Added footnote in Sec. IIIB
Added reference in Sec. IIIB
Added footnote in Sec. IV
Modified Sec. V

### 2022-11-02 resub_PRB/Paper1.tex
Modified Paolos addenda in the paper and the replies to the referees.

For this goal we consider the simplified model shown in Fig.~\ref{fig:setup}, consisting of a Hubbard layer located between two leads. The leads have themselves a wide band, as expected for good conductors, which is effectively narrowed due to the weak coupling to intermediate layers which we take as simplified models for the contacts. Electrons on the Hubbard layer interact locally with acoustic phonons. An external periodic electric field induces a Floquet steady state with a current flowing from the lead with the lower to the lead with the higher chemical potential, thus transferring its energy.
 We address this periodic problem via nonequilibrium Floquet dynamical mean-field theory (F-DMFT) \resub{, which has been proven to give meaningful results in similar setups (see, e.g.~\cite{so.do.18}) and when spatially non-local correlations as long-range magnetic fluctuations are explicitly not taken into account~\cite{ro.ha.18}.}

@@

Our setup introduced in Sec.~\ref{sec:intro} and shown in Fig.~\ref{fig:setup} is described by the Hamiltonian
%
\begin{equation}
\label{eq:Hamiltonian}
\begin{split} 
\hat{H}(t)&=\varepsilon_{\text{c}} \sum_{i\sigma}\hat{n}_{i\sigma} -\sum_{\sigma}\sum_{(i,j)} t_{ij}(t) \hat{c}^{\dagger}_{i\sigma} \hat{c}_{j\sigma}
\\ & + U \sum_{i} \hat{n}_{i\uparrow} \hat{n}_{i\downarrow}+\hat{H}_{\text{e-ph}} + \hat{H}_{\text{ph}}+\hat{H}_{\text{lead}}.
\end{split}
\end{equation}
% 
The operator $\hat{c}^{\dagger}_{i\sigma}$ ($\hat{c}_{i\sigma}$) creates (annihilates) an electron with spin $\sigma= \lbrace \uparrow,\downarrow \rbrace$ on the $i$-th lattice site and $\hat{n}_{i\sigma}\equiv \hat{c}^{\dagger}_{i\sigma} \hat{c}_{i\sigma}$ is the particle number operator. We denote with $(i,j)$ the sum over nearest-neighbor sites and with $\varepsilon_{\text{c}} \equiv -U/2$ the on-site energy. The driving field consists of a time-periodic, homogeneous and monochromatic electric field with frequency $\Omega$. In the temporal gauge it enters via the Peierls substitution in the time-dependent hopping in Eq.~\eqref{eq:Hamiltonian}~\cite{peie.33}

\begin{equation}\label{eq:peierls} 
t_{ij}(t) = t_{\text{c}} \ e^{-\ii \frac{q}{\hbar} \left( \vec{r}_j - \vec{r}_i \right) \cdot \vec{A}(t)}, 
\end{equation}
% 
where $t_{\text{c}}$ is the intra-layer hopping, $\vec{A}$(t) the time-dependent vector potential, $\hbar$ Planck's constant and $q$ the charge of the electrons. Following Refs.~\cite{ts.ok.08,mu.we.18}, we choose for simplicity
 $\vec{A}(t)=\vec{e}_{0} A(t)$, which points along the 
lattice body diagonal $\vec{e}_{0}=(1,1,\dots,1)$. Therein $A(t)=\frac{\hbar}{qa}\aamp\sin(\Omega t)$ with $\aamp=-\frac{qE_0a}{\hbar\Omega}$, $E_0$ is the electric field amplitude, and $a$ the lattice spacing~\cite{ts.ok.08}. 
In this temporal gauge the electric field is $\vec{E}= -\partial_{t}\vec{A}(t) = \vec{e}_{0}E_0 \cos(\Omega t)$.

As in Ref.~\cite{ma.ga.22}, phonons are included in the form of acoustic  branches attached to each lattice site and coupled to the electrons via the Hamiltonian 
\begin{equation}\label{eq:e-ph_ham} 
\hat{H}_{\text{e-ph}} = g \sum_{i\sigma} \hat{n}_{i\sigma} \hat{x}_{i},  
\end{equation}
with $g$ as e-ph coupling and $\hat{x}_{i} \equiv \frac{1}{\sqrt{2}} \left( \hat{b}^{\dagger}_{i} + \hat{b}_i \right)$, where $\hat{b}^{\dagger}_{i}$ ($\hat{b}_{i}$) creates (annihilates) a phonon of the acoustic branch at site $i$, with dispersion relation described by $\hat{H}_{\text{ph}}$, discussed in Sec~\ref{sec:Dyson_equation}. In contrast to Holstein phonons, they have a finite bandwidth, which is more effective in energy dissipation. Details on the leads are provided in Sec.~\ref{sec:Dyson_equation}.

For mathematical simplicity~\cite{ge.ko.92,ao.ts.14}, 
 we consider the correlated central region as a $d$-dimensional layer and consider the limit of infinite dimensions $d \rightarrow \infty$ by rescaling the hopping as $t_{\text{c}}=t^{\ast}/(2\sqrt{d})$. Taking $a=1$, sums over the crystal momentum ${\bf k}$ of a generic quantity $\chi$ read $\sum_{{\bf k}} \chi(\omega,{\bf k}) \rightarrow \int d\epsilon \int   d\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \chi(\omega;\epsilon,\overline{\epsilon})$ with $\rho(\epsilon,\overline{\epsilon}) = (1/\pi t^{\ast 2}) \exp[-( \epsilon^{2} + \overline{\epsilon}^{2})/t^{\ast 2}]$ as the joint density of states~\cite{ts.ok.08} and with
% 
\begin{align}\label{eq:d-dim_crystal_dep}
\begin{split}  
\epsilon & = -2t_{\text{c}} \sum_{i=1}^{d} \cos(k_i a), \\  
\overline{\epsilon}& = -2t_{\text{c}}\sum_{i=1}^{d} \sin(k_i a). \\
\end{split}  
\end{align}
%

@@

To correctly describe the nonequilibrium periodic steady state, we use the Floquet generalization of the nonequilibrium Green's function (NEGF) 
approach~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}. Every function $G(t,t^{\prime})$ satisfying the periodicity relation $G(t,t^{\prime})=G(t+\tau,t^{\prime}+\tau)$, with $\tau=2\pi/\Omega$ as the period related to the external driving frequency $\Omega$, may be represented as~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}

\begin{equation}
\label{eq:FloquetGF} 
\underline{G}_{mn}(\omega) =\int \dd t_{\text{rel}} \int_{-\tau/2}^{\tau/2} \frac{dt_{\text{av}}}{\tau} \ee^{\ii[\left(\omega+m\Omega\right) t -\left( \omega+n\Omega\right)t^{\prime}]} \underline{G}(t,t'),
\end{equation}
known as the \emph{Keldysh-Floquet} GF. The integration variables $t_{\text{rel}} = t-t^{\prime}$ and $t_{\text{av}} = (t+t^{\prime})/2$ are the relative and average times. Within the rest of this work, we denote a Floquet-represented matrix either as $X_{mn}$ with explicit indices, or use a boldface letter $\bf{X}$. The underline indicates the overall \emph{Keldysh} structure
%
\begin{equation}\label{eq:Keld-structure}
\underline{{\bf G}} \equiv 
\begin{pmatrix}
{\bf G}^{\text{R}} & {\bf G}^{\text{K}}\\
{\bf 0}         & {\bf G}^{\text{A}} \\
\end{pmatrix},
\end{equation}
%
which contains the \emph{retarded}, \emph{advanced} and \emph{Keldysh} components $\textbf{G}^{\text{R,A,K}}$, where $\textbf{G}^{\text{A}}=(\textbf{G}^{\text{R}})^{\dagger}$. The \emph{Keldysh} component is defined as $\textbf{G}^{\text{K}} \equiv \textbf{G}^{>} + \textbf{G}^{<}$, with $\textbf{G}^{\lessgtr}$ as \emph{lesser} and \emph{greater} components~\cite{schw.61,keld.65,ra.sm.86,ha.ja}.

@@

The lattice Floquet GF of our setup obeys the Dyson equation 
\begin{equation}\label{eq:FullDysonEq}
\underline{{\bf G}}^{-1}(\omega_n;\epsilon,\overline{\epsilon}) = \underline{{\bf G}}^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}(\omega_n;\epsilon,\overline{\epsilon}) - \underline{{\bf \Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon}),
\end{equation}
where in our approximation the electron self-energy (SE) $ \underline{{\bf \Sigma}}$ and e-ph SE $\underline{{\bf \Sigma}}_{\text{e-ph}}$ contribute independently to the total SE~\footnote{In fact, there is an indirect feedback via the DMFT self-consistency.}.

Therein, the lattice GF of the non-interacting part of the Hamiltonian in Eq.~\eqref{eq:Hamiltonian} is

\begin{equation}\label{eq:non-int_InvGF} 
\underline{G}^{-1}_{0,mn}(\omega_n;\epsilon,\overline{\epsilon}) =  \underline{g}^{-1}_{0,mn}(\omega_n;\epsilon,\overline{\epsilon}) - \sum_{\rho\in\{\text{l},\text{r}\}}v^2_{\rho}\underline{g}_{\text{b},\rho}(\omega_n;\epsilon)\delta_{mn}
\end{equation}
with $v_{\text{l}/\text{r}}$ as lead-layer hybridization, $\omega_n \equiv \omega + n\Omega$, $n\in\mathbbm{Z}$, and 
%
\begin{equation}\label{eq:inv_non-int_lat_GF_comps}
\begin{split}
\left[ g^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon})) \right]^{\text{R}}_{mn} & = \left( \omega_n + i0^{+} -\varepsilon_{\text{c}} \right)\delta_{mn} - \varepsilon_{mn}(\epsilon,\overline{\epsilon}), \\
\left[ g^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon})) \right]^{\text{K}}_{mn} & = 0
\end{split}
\end{equation}
%
as the noninteracting Green's function of the isolated layer, whose inverse Keldysh component is negligible in the steady state. The Floquet dispersion relation $\varepsilon_{mn}$ for the periodic field in a hyper-cubic lattice is~\cite{ts.ok.08} 
%
\begin{equation}
\label{eq:Floquet_disp}
\varepsilon_{mn}(\epsilon,\overline{\epsilon}) = \begin{cases}
\epsilon J_{m-n}(\aamp) & m-n:\text{even}, \\
\ii\overline{\epsilon}J_{m-n}(\aamp) & m-n:\text{odd},
\end{cases}
\end{equation} 
%  
where $J_n$ denotes the $n$-th order Bessel function of the first kind, with the argument $\aamp$ defined in Sec.~\ref{sec:Model}. The  GF $\underline{g}_{\text{b},\text{l}/\text{r}}$ on the $d$-dimensional boundary of the decoupled leads,  consisting of a single layer coupled to a semi-infinite reservoir in the wide-band limit with broadening $\Gamma_{\text{l}/\text{r}}$ (cf. Fig.~\ref{fig:setup}) is given by
%  
\begin{align}
g^{\text{R}}_{\text{b},\text{l}/\text{r}}(\omega;\epsilon) &= \frac{1}{\omega-\varepsilon_{\text{l}/\text{r}}(\epsilon)+\ii\Gamma_{\text{l}/\text{r}}},\label{eq:retarded_bath_GF} \\
g^{\text{K}}_{\text{b},\text{l}/\text{r}}(\omega;\epsilon) &= 2\ii \iim[g_{\text{b},\text{l}/\text{r}}^{\text{R}}(\omega;\epsilon)][1-2f(\omega,\mu_{\text{l}/\text{r}},\beta)], \label{eq:keldysh_bath_GF}
\end{align} 
%
where $\varepsilon_{\text{l}/\text{r}}(\epsilon)=\varepsilon_{\text{l}/\text{r}} +\frac{t_{\text{l}/\text{r}}}{t^\ast}\epsilon$ is the dispersion, $f(\omega,\mu_{\text{l}/\text{r}},\beta)=1/[\ee^{\beta(\omega-\mu_{\text{l}/\text{r}})}+1]$ the Fermi-Dirac distribution function at inverse temperature $\beta \equiv 1/T$, $\varepsilon_{\text{l}/\text{r}}$ the onsite energy and $t_{\text{l}/\text{r}}$ the hopping within the $d$-dimensional layer of the lead.

The electron SE $\underline{\bf{\Sigma}}$ is obtained from F-DMFT and therefore, in this approximation, independent of the crystal momentum, i.e. $\underline{\bf{\Sigma}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}(\omega)$. Further details are given in Sec.~\ref{sec:FDMFT_implementation}. In the same spirit, the e-ph SE is included locally as $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ ~\footnote{\resub{As explicitly stated in Sec.~\ref{sec:intro}, our analysis provides only qualitative results. A more accurate treatment that aims to provide quantitative predictions, should take into account the crystal momentum dependence of $\underline{\bf{\Sigma}}_{\text{e-ph}}$. We refer to the review~\cite{gius.17} for a detailed and comprehensive explanation.}}. In terms of the Keldysh contour time arguments $z$ and $z^\prime$, it has the form

\begin{equation}\label{eq:backbone_e-ph_SE}
\Sigma_{\text{e-ph}}(z,z^{\prime}) = \ii g^{2} G(z,z^{\prime}) D_{\text{ph}}(z,z^{\prime}).
\end{equation}

>>>>

For this goal we consider the simplified model shown in Fig.~\ref{fig:setup}, consisting of a Hubbard layer located between two leads. The leads have themselves a wide band, as expected for good conductors, which is effectively narrowed due to the weak coupling to intermediate layers which we take as simplified models for the contacts. Electrons on the Hubbard layer interact locally with acoustic phonons. An external periodic electric field induces a Floquet steady state with a current flowing from the lead with the lower to the lead with the higher chemical potential, thus transferring its energy. We address this periodic problem via nonequilibrium Floquet dynamical mean-field theory (F-DMFT)\resub{, which has been shown to give meaningful results in similar setups (see, e.g.~\cite{so.do.18}). Since we are not interested in capturing long-ranged collective excitations, non-local correlations~\cite{ro.ha.18} are not taken into account.}

@@

Our setup introduced in Sec.~\ref{sec:intro} and shown in Fig.~\ref{fig:setup} is described by the Hamiltonian
%
\begin{equation}
\label{eq:Hamiltonian}
\begin{split} 
\hat{H}(t)&=\varepsilon_{\text{c}} \sum_{i\sigma}\hat{n}_{i\sigma} -\sum_{\sigma}\sum_{(i,j)} t_{ij}(t) \hat{c}^{\dagger}_{i\sigma} \hat{c}_{j\sigma}
\\ & + U \sum_{i} \hat{n}_{i\uparrow} \hat{n}_{i\downarrow}+\hat{H}_{\text{e-ph}} + \hat{H}_{\text{ph}}+\hat{H}_{\text{lead}}.
\end{split}
\end{equation}
% 
The operator $\hat{c}^{\dagger}_{i\sigma}$ ($\hat{c}_{i\sigma}$) creates (annihilates) an electron with spin $\sigma= \lbrace \uparrow,\downarrow \rbrace$ on the $i$-th lattice site and $\hat{n}_{i\sigma}\equiv \hat{c}^{\dagger}_{i\sigma} \hat{c}_{i\sigma}$ is the particle number operator. We denote with $(i,j)$ the sum over nearest-neighbor sites and with $\varepsilon_{\text{c}} \equiv -U/2$ the on-site energy. The driving field consists of a time-periodic, homogeneous and monochromatic electric field with frequency $\Omega$. In the temporal gauge it enters via the Peierls substitution in the time-dependent hopping in Eq.~\eqref{eq:Hamiltonian}~\cite{peie.33}
% 
\begin{equation}\label{eq:peierls} 
t_{ij}(t) = t_{\text{c}} \ e^{-\ii \frac{q}{\hbar} \left( \vec{r}_j - \vec{r}_i \right) \cdot \vec{A}(t)}, 
\end{equation}
% 
where $t_{\text{c}}$ is the intra-layer hopping, $\vec{A}$(t) the time-dependent vector potential, $\hbar$ Planck's constant and $q$ the charge of the electrons. Following Refs.~\cite{ts.ok.08,mu.we.18}, we choose for simplicity $\vec{A}(t)=\vec{e}_{0} A(t)$, which points along the lattice body diagonal $\vec{e}_{0}=(1,1,\dots,1)$. Therein $A(t)=\frac{\hbar}{qa}\aamp\sin(\Omega t)$ with $\aamp=-\frac{qE_0a}{\hbar\Omega}$, $E_0$ is the electric field amplitude, and $a$ the lattice spacing~\cite{ts.ok.08}. 
In this temporal gauge the electric field is $\vec{E}= -\partial_{t}\vec{A}(t) = \vec{e}_{0}E_0 \cos(\Omega t)$.

As in Ref.~\cite{ma.ga.22}, phonons are included in the form of acoustic  branches attached to each lattice site and coupled to the electrons via the Hamiltonian 
% 
\begin{equation}\label{eq:e-ph_ham} 
\hat{H}_{\text{e-ph}} = g \sum_{i\sigma} \hat{n}_{i\sigma} \hat{x}_{i},
\end{equation}
% 
with $g$ as e-ph coupling and $\hat{x}_{i} \equiv \frac{1}{\sqrt{2}} \left( \hat{b}^{\dagger}_{i} + \hat{b}_i \right)$, where $\hat{b}^{\dagger}_{i}$ ($\hat{b}_{i}$) creates (annihilates) a phonon of the acoustic branch at site $i$, with dispersion relation described by $\hat{H}_{\text{ph}}$, discussed in Sec~\ref{sec:Dyson_equation}. In contrast to Holstein phonons, they have a finite bandwidth, which is more effective in energy dissipation. Details on the leads are provided in Sec.~\ref{sec:Dyson_equation}.

For mathematical simplicity~\cite{ge.ko.92,ao.ts.14}, we consider the correlated central region as a $d$-dimensional layer and consider the limit of infinite dimensions $d \rightarrow \infty$ by rescaling the hopping as $t_{\text{c}}=t^{\ast}/(2\sqrt{d})$. Taking $a=1$, sums over the crystal momentum $\vec{k}$ of a generic quantity $\chi$ read $\sum_{\vec{k}} \chi(\omega,\vec{k}) \rightarrow \int \dd\epsilon \int   \dd\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \chi(\omega;\epsilon,\overline{\epsilon})$ with $\rho(\epsilon,\overline{\epsilon}) = (1/\pi t^{\ast 2}) \exp[-( \epsilon^{2} + \overline{\epsilon}^{2})/t^{\ast 2}]$ as the joint density of states~\cite{ts.ok.08} and with
% 
\begin{align}\label{eq:d-dim_crystal_dep}
\begin{split}
\epsilon & = -2t_{\text{c}} \sum_{i=1}^{d} \cos(k_i a), \\  
\overline{\epsilon}& = -2t_{\text{c}}\sum_{i=1}^{d} \sin(k_i a). \\
\end{split}  
\end{align}

@@

To correctly describe the nonequilibrium periodic steady state, we use the Floquet generalization of the nonequilibrium Green's function (NEGF) approach~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}. Every function $G(t,t^{\prime})$ satisfying the periodicity relation $G(t,t^{\prime})=G(t+\tau,t^{\prime}+\tau)$, with $\tau=2\pi/\Omega$ as the period related to the external driving frequency $\Omega$, may be represented as~\cite{ts.ok.08,sc.mo.02u,jo.fr.08}
% 
\begin{equation}
\label{eq:FloquetGF} 
\kel{G}_{mn}(\omega) =\int \dd t_{\text{rel}} \int_{-\tau/2}^{\tau/2} \frac{\dd t_{\text{av}}}{\tau} \ee^{\ii[\left(\omega+m\Omega\right) t -\left( \omega+n\Omega\right)t^{\prime}]} \kel{G}(t,t'),
\end{equation}
% 
known as the \emph{Keldysh-Floquet} GF. The integration variables $t_{\text{rel}} = t-t^{\prime}$ and $t_{\text{av}} = (t+t^{\prime})/2$ are the relative and average times. Within the rest of this work, we denote a Floquet-represented matrix either as $X_{mn}$ with explicit indices, or use a boldface letter $\mat{X}$. The underline indicates the overall \emph{Keldysh} structure
%
\begin{equation}\label{eq:Keld-structure}
\kel{\mat{G}} \equiv
\begin{pmatrix}
\mat{G}^{\text{R}} & \mat{G}^{\text{K}}\\
\mat{0}            & \mat{G}^{\text{A}} \\
\end{pmatrix},
\end{equation}
%
which contains the \emph{retarded}, \emph{advanced} and \emph{Keldysh} components $\mat{G}^{\text{R,A,K}}$, where $\mat{G}^{\text{A}}=(\mat{G}^{\text{R}})^{\dagger}$. The \emph{Keldysh} component is defined as $\mat{G}^{\text{K}} \equiv \mat{G}^{>} + \mat{G}^{<}$, with $\mat{G}^{\lessgtr}$ as \emph{lesser} and \emph{greater} components~\cite{schw.61,keld.65,ra.sm.86,ha.ja}.

@@

The lattice Floquet GF of our setup obeys the Dyson equation 
% 
\begin{equation}\label{eq:FullDysonEq}
\kel{\mat{G}}^{-1}(\omega_n;\epsilon,\overline{\epsilon}) = \kel{\mat{G}}^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon}) - \kel{\mat{\Sigma}}(\omega_n;\epsilon,\overline{\epsilon}) - \kel{\mat{\Sigma}}_{\text{e-ph}}(\omega_n;\epsilon,\overline{\epsilon}),
\end{equation}
% 
where in our approximation the electron self-energy (SE) $ \kel{\mat{\Sigma}}$ and e-ph SE $\kel{\mat{\Sigma}}_{\text{e-ph}}$ contribute independently to the total SE~\footnote{In fact, there is an indirect feedback via the DMFT self-consistency.}. Therein, the lattice GF of the non-interacting part of the Hamiltonian in Eq.~\eqref{eq:Hamiltonian} is 
% 
\begin{equation}\label{eq:non-int_InvGF} 
\kel{G}^{-1}_{0,mn}(\omega_n;\epsilon,\overline{\epsilon}) =  \kel{g}^{-1}_{0,mn}(\omega_n;\epsilon,\overline{\epsilon}) - \sum_{\rho\in\{\text{l},\text{r}\}}v^2_{\rho}\kel{g}_{\text{b},\rho}(\omega_n;\epsilon)\delta_{mn}
\end{equation}
% 
with $v_{\text{l}/\text{r}}$ as lead-layer hybridization, $\omega_n \equiv \omega + n\Omega$, $n\in\mathbbm{Z}$, and 
%
\begin{equation}\label{eq:inv_non-int_lat_GF_comps}
\begin{split}
\left[ g^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon})) \right]^{\text{R}}_{mn} & = \left( \omega_n + i0^{+} -\varepsilon_{\text{c}} \right)\delta_{mn} - \varepsilon_{mn}(\epsilon,\overline{\epsilon}), \\
\left[ g^{-1}_{0}(\omega_n;\epsilon,\overline{\epsilon})) \right]^{\text{K}}_{mn} & = 0
\end{split}
\end{equation}
%
as the noninteracting Green's function of the isolated layer, whose inverse Keldysh component is negligible in the steady state. The Floquet dispersion relation $\varepsilon_{mn}$ for the periodic field in a hyper-cubic lattice is~\cite{ts.ok.08} 
%
\begin{equation}
\label{eq:Floquet_disp}
\varepsilon_{mn}(\epsilon,\overline{\epsilon}) = \begin{cases}
\epsilon J_{m-n}(\aamp) & m-n:\text{even}, \\
\ii\overline{\epsilon}J_{m-n}(\aamp) & m-n:\text{odd},
\end{cases}
\end{equation} 
%  
where $J_n$ denotes the $n$-th order Bessel function of the first kind, with the argument $\aamp$ defined in Sec.~\ref{sec:Model}. The  GF $\kel{g}_{\text{b},\text{l}/\text{r}}$ on the $d$-dimensional boundary of the decoupled leads,  consisting of a single layer coupled to a semi-infinite reservoir in the wide-band limit with broadening $\Gamma_{\text{l}/\text{r}}$ (cf. Fig.~\ref{fig:setup}) is given by
%  
\begin{align}
g^{\text{R}}_{\text{b},\text{l}/\text{r}}(\omega;\epsilon) &= \frac{1}{\omega-\varepsilon_{\text{l}/\text{r}}(\epsilon)+\ii\Gamma_{\text{l}/\text{r}}},\label{eq:retarded_bath_GF} \\
g^{\text{K}}_{\text{b},\text{l}/\text{r}}(\omega;\epsilon) &= 2\ii \iim[g_{\text{b},\text{l}/\text{r}}^{\text{R}}(\omega;\epsilon)][1-2f(\omega,\mu_{\text{l}/\text{r}},\beta)], \label{eq:keldysh_bath_GF}
\end{align} 
%
where $\varepsilon_{\text{l}/\text{r}}(\epsilon)=\varepsilon_{\text{l}/\text{r}} +\frac{t_{\text{l}/\text{r}}}{t^\ast}\epsilon$ is the dispersion, $f(\omega,\mu_{\text{l}/\text{r}},\beta)=1/[\ee^{\beta(\omega-\mu_{\text{l}/\text{r}})}+1]$ the Fermi-Dirac distribution function at inverse temperature $\beta \equiv 1/T$, $\varepsilon_{\text{l}/\text{r}}$ the onsite energy and $t_{\text{l}/\text{r}}$ the hopping within the $d$-dimensional layer of the lead.

The electron SE $\kel{\mat{\Sigma}}$ is obtained from F-DMFT and therefore, in this approximation, independent of the crystal momentum, i.e. $\kel{\mat{\Sigma}}(\omega;\epsilon,\overline{\epsilon}) \simeq \kel{\mat{\Sigma}}(\omega)$. Further details are given in Sec.~\ref{sec:FDMFT_implementation}. In the same spirit, the e-ph SE is included locally as $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$~\footnote{\resub{As stated in Sec.~\ref{sec:intro}, our analysis provides only qualitative results. A more accurate treatment that aims to provide quantitative predictions, should take into account the crystal momentum dependence of $\kel{\mat{\Sigma}}_{\text{e-ph}}$. We refer to the review~\cite{gius.17} which discusses the effects of phonons on the electronic bandstructure and the modelling thereof.}}\vphantom{\cite{gius.17}}. In terms of the Keldysh contour time arguments $z$ and $z^\prime$, it has the form      
% 
\begin{equation}\label{eq:backbone_e-ph_SE}
\Sigma_{\text{e-ph}}(z,z^{\prime}) = \ii g^{2} G(z,z^{\prime}) D_{\text{ph}}(z,z^{\prime}).
\end{equation}
% 
The Keldysh components of the non-interacting phonon GF $\kel{D}_{\text{ph}}(t,t^{\prime})$ are given by~\cite{ao.ts.14}
%
\begin{align}\label{eq:Ph_Prop_time}
\begin{split} 
D^{\text{R}}_{\text{ph}}(t,t^{\prime}) & = -\ii \theta(t-t^{\prime}) \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega), \\
D^{>}_{\text{ph}}(t,t^{\prime}) & = -\ii \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega) \left[ 1 + b(\omega) \right] \\
D^{<}_{\text{ph}}(t,t^{\prime}) & = -\ii \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega) \ b(\omega), \\
\end{split}, 
\end{align}
%
where $b(\omega)=1/(\ee^{\beta\omega}-1)$ is the Bose-Einstein distribution function at inverse temperature $\beta$. We consider acoustic phonons, with spectral function $A_{\text{ph}}(\omega) = (\omega/\omega^{2}_{\text{ph}}) \ee^{-| \omega|/\omega_{\text{ph}}}$,  $\omega_{\text{ph}}$ being a soft cutoff frequency~\cite{pi.li.21}. The retarded and Keldysh components of the e-ph SE are easily extracted from  Eq.~\eqref{eq:backbone_e-ph_SE} and can be found in Ref.~\cite{ma.ga.22}.
